Algebraic File Synchronization: Adequacy and Completeness

### 2017-11-05 p2/paper.tex
More TODO

@@

% TODO Add reviewer
% TODO Consider below
I thank L. Csirmaz for his invaluable input on this paper,
and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.

>>>>

TODO: $|[D]|=1$ - where used? Can we move $A \cap B$ to the beginning?

% A: <D1,D2,n'>
% B: <D1,D3,n'> <empt,F,n>
% Reconciliation does not create file, but we can create it -> reconciliation maximal not true.

TODO: After reconciliation, subsequence order works.

@@

I thank Laszlo Csirmaz for his invaluable input on this paper,
and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.
